### 2015-12-07 paper/4-performance.tex
typo

\subsection{Parallel Simulation}
%TODO explain that we will now compare different synchronization protocols
%TODO compare different synchronization protocols with adevs' conservative, showing that we are faster (or at least, not that much slower) than adevs
By default, the benchmarks use 4 kernels for parallel simulation.
\subsubsection{Devstone}
The flattened models are allocated to kernels by giving each kernel a distinct section of the chain, resulting in a low ratio of inter-kernel to intra-kernel messages. For the optimistic case, this can cause more reverts since the kernels will start to drift faster as the model-count increases. Furthermore, optimistic synchronization is quite sensitive to an increase in kernels, since the delay before a revert propagates, increases. This benchmark requires a specific warm-up time; for $n=d\times w$ models, it takes $\textup{timeadvance}()*(n-1)$ transitions to activate the last model in the chain. When using parallel processing, this can be reduced to $\textup{timeadvance}()*(n\frac{kernels-1}{kernels} -1)$ before the last kernel becomes active.\\
Figure~\cite{fig:DevstonParallel} shows that dxex outperformance adevs (in both optimistic and conservative case).
\begin{figure}[ltbh]
	\includegraphics[width=.5\textwidth]{fig/fig2.eps}
	\label{fig:DevstoneParallel}
	\caption{DevStone parallel}
\end{figure}
\subsubsection{PHold}
%Phold
In Phold, the allocation is specified in the benchmark itself. Each kernel manages a single node with a constant set of sub-nodes. The parameter $R$ (which is here set to $10$) determines the percentage of remote destination models.\\
The dynamic dependency graph is a very sparse version of the static dependency graph, penalizing the conservative case. The lookahead is $\epsilon$, so the conservative case spends most of its time crawling in steps of $\epsilon$. Since the dependency graph between kernels is a complete graph, this is not a simulation that scales in our implementation. For $N$ kernels, each kernel has to query the null-time of $N-1$ kernels, resulting in O($N^2$) polling behaviour. In a non-cyclic simulation with a non-trivial lookahead (like in, e.g., Devstone), that choice does pay off (see Figure~\ref{fig:DevstoneParallel}). Adevs's lesser performance is due in part to their lookahead management, which after profiling shows to spend a non-trivial amount of time in exception handling code.\\
The optimistic case suffers little from the above problems; due to the high interconnectivity, however, a cascading revert is still possible. With the percentage of remotes equal to $100$, Phold reflects interconnect in behaviour, which is why the $R$ value is not dimensioned here. A revert is very expensive in PHold due to our usage of C++11's random nr generators. The cost of a revert is dominated by the recalculation of destination models, not in allocating/deallocating states/messages. Once a revert happens the drift between kernels increases fast, increasing the likelihood of more reverts. Despite all this, optimistic can for low $R$ values quickly exploit the uncertainty that slows down conservative in this benchmark.

>>>>

\subsection{Parallel Simulation}
%TODO explain that we will now compare different synchronization protocols
%TODO compare different synchronization protocols with adevs' conservative, showing that we are faster (or at least, not that much slower) than adevs
By default, the benchmarks use 4 kernels for parallel simulation.
\subsubsection{Devstone}
The flattened models are allocated to kernels by giving each kernel a distinct section of the chain, resulting in a low ratio of inter-kernel to intra-kernel messages. For the optimistic case, this can cause more reverts since the kernels will start to drift faster as the model-count increases. Furthermore, optimistic synchronization is quite sensitive to an increase in kernels, since the delay before a revert propagates, increases. This benchmark requires a specific warm-up time; for $n=d\times w$ models, it takes $\textup{timeadvance}()*(n-1)$ transitions to activate the last model in the chain. When using parallel processing, this can be reduced to $\textup{timeadvance}()*(n\frac{kernels-1}{kernels} -1)$ before the last kernel becomes active.\\
Figure~\ref{fig:DevstoneParallel} shows that dxex outperformance adevs (in both optimistic and conservative case).
\begin{figure}[ltbh]
	\includegraphics[width=.5\textwidth]{fig/fig2.eps}
	\label{fig:DevstoneParallel}
	\caption{DevStone parallel}
\end{figure}
\subsubsection{PHold}
%Phold
In Phold, the allocation is specified in the benchmark itself. Each kernel manages a single node with a constant set of sub-nodes. The parameter $R$ (which is here set to $10$) determines the percentage of remote destination models.\\
The dynamic dependency graph is a very sparse version of the static dependency graph, penalizing the conservative case. The lookahead is $\epsilon$, so the conservative case spends most of its time crawling in steps of $\epsilon$. Since the dependency graph between kernels is a complete graph, this is not a simulation that scales in our implementation. For $N$ kernels, each kernel has to query the null-time of $N-1$ kernels, resulting in O($N^2$) polling behaviour. In a non-cyclic simulation with a non-trivial lookahead (like in, e.g., Devstone), that choice does pay off (see Figure~\ref{fig:DevstoneParallel}). Adevs's lesser performance is due in part to their lookahead management, which after profiling shows to spend a non-trivial amount of time in exception handling code.\\
The optimistic case suffers little from the above problems; due to the high interconnectivity, however, a cascading revert is still possible. With the percentage of remotes equal to $100$, Phold reflects interconnect in behaviour, which is why the $R$ value is not dimensioned here. A revert is very expensive in PHold due to our usage of C++11's random nr generators. The cost of a revert is dominated by the recalculation of destination models, not in allocating/deallocating states/messages. Once a revert happens the drift between kernels increases fast, increasing the likelihood of more reverts. Despite all this, optimistic can for low $R$ values quickly exploit the uncertainty that slows down conservative in this benchmark.
